CTFEF

### 2023-08-28 Papers/FEDCIS-2023-presentation/cm1.tex
some stuff

\documentclass[10pt,xcolor=svgnames]{beamer} %Beamer
\usepackage{palatino} %font type
\usepackage{caption}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{csquotes}

\usefonttheme{metropolis} %Type of slides
\usefonttheme[onlymath]{serif} %font type Mathematical expressions
\usetheme[progressbar=frametitle,titleformat frame=smallcaps,numbering=counter]{metropolis} %This adds a bar at the beginning of each section.
\useoutertheme[subsection=false]{miniframes} %Circles in the top of each frame, showing the slide of each section you are at

\usepackage{appendixnumberbeamer} %enumerate each slide without counting the appendix
\setbeamercolor{progress bar}{fg=Maroon!70!Coral} %These are the colours of the progress bar. Notice that the names used are the svgnames
\setbeamercolor{title separator}{fg=DarkSalmon} %This is the line colour in the title slide
\setbeamercolor{structure}{fg=black} %Colour of the text of structure, numbers, items, blah. Not the big text.
\setbeamercolor{normal text}{fg=black!87} %Colour of normal text
\setbeamercolor{alerted text}{fg=DarkRed!60!Gainsboro} %Color of the alert box
\setbeamercolor{example text}{fg=Maroon!70!Coral} %Colour of the Example block text

\setbeamercolor{palette primary}{bg=NavyBlue!50!DarkOliveGreen, fg=white} %These are the colours of the background. Being this the main combination and so one.
\setbeamercolor{palette secondary}{bg=NavyBlue!50!DarkOliveGreen, fg=white}
\setbeamercolor{palette tertiary}{bg=NavyBlue!40!Black, fg= white}
\setbeamercolor{section in toc}{fg=NavyBlue!40!Black} %Color of the text in the table of contents (toc)

@@

\lstloadlanguages{C,C++,csh,Java}

@@

\setbeamercolor{background canvas}{bg=NavyBlue!50!DarkOliveGreen, fg=white}
\setbeamercolor{normal text}{fg=white}
\maketitle
}%This is the colour of the first slide. bg= background and fg=foreground

@@

\input{sections/motivation.tex}

>>>>

\documentclass[10pt]{beamer} %Beamer

\usepackage{palatino} %font type
\usepackage{caption}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{csquotes}

\usepackage{appendixnumberbeamer} %enumerate each slide without counting the appendix

@@

\lstloadlanguages{C,C++,csh,Java}
\usefonttheme{metropolis} %Type of slides
\usefonttheme[onlymath]{serif} %font type Mathematical expressions
\usetheme[progressbar=frametitle,titleformat frame=smallcaps,numbering=counter]{metropolis} %This adds a bar at the beginning of each section.
\useoutertheme[subsection=false]{miniframes} %Circles in the top of each frame, showing the slide of each section you are at

@@

\maketitle
}%This is the colour of the first slide. bg= background and fg=foreground

@@

\input{sections/motivation.tex}
\input{sections/CTFEF.tex}

### 2023-08-28 Papers/FEDCIS-2023-presentation/sections/motivation.tex
some stuff

>>>>

\begin{frame}
	\frametitle{C-=-1}

	\begin{itemize}
		\item General purpose, compiled research programming language with manual memory management
		\item Built around powerful static metaprogramming features
		\item Arbitrary code can be executed at compile time\begin{itemize}
			\item Inspect the code base and report diagnostics
			\item Access semantic information generated by the compiler
			\item Modify the program before it is translated to machine code
			\item Access the file system and external tools
		\end{itemize}
	\end{itemize}

\begin{frame}
	\frametitle{C-=-1}

	\begin{itemize}
		\item General purpose, compiled research programming language with manual memory management
		\item Built around powerful static metaprogramming features
		\item Arbitrary code can be executed at compile time\begin{itemize}
			\item Inspect the code base and report diagnostics
			\item Modify the program before it is translated to machine code
			\item Access the file system and external tools
		\end{itemize}
	\end{itemize}
